DeepSphere: a graph-based spherical CNN

### 2019-11-12 main.tex
Updates from Overleaf

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\renewcommand{\b}[1]{{\bm{#1}}}  % bold symbol
\newcommand{\bO}{\mathcal{O}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\S}{\mathbb{S}}
\newcommand{\G}{\mathcal{G}}  % graph
\newcommand{\V}{\mathcal{V}}  % vertex set
\newcommand{\E}{\mathcal{E}}  % edge set
\newcommand{\laplacian}{\Delta_{\mathbb S^2}}
\newcommand{\Rg}{\mathcal R_g}
\newcommand{\seminorm}[1]{\left|#1\right|}
\newcommand{\Ln}{L_n^{t_n}}

@@

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. \mart{Here we insert the definition of the extended graph laplacian and of the rotation operator Rg} Following their setting, we define the extended graph Laplacian operator as a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$. Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere 
\begin{equation}\label{eq:rotation operator}
\mathcal R_g f(x) := f(g^{-1}(x)).
\end{equation}
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
	\end{equation*} 
% 	for $n\to\infty$.
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, $\b{L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}. \mart{here we insert the link between consistency and equivariance} This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{prop}\label{prop:equivariance}
Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence
\begin{equation*}
\forall x\in\mathbb S^2\quad\left| \mathcal R_g L_n^{t_n} f (x) - L_n^{t_n} \mathcal R_g f(x) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{prop}
%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Proof of proposition \ref{prop:equivariance}}
\begin{proof}
Fix $x\in \mathbb S^2$. Since any rotation $\mathcal R_g$ is an isometry, and the Laplacian $\Delta$ commutes with all isometries of a Riemanniann manifold \cite{shubin}, and defining $\mathcal R_g f =: f'$ for ease of notation, we can write that 
	\begin{align*}
			\seminorm{\Rg \Ln f (x) - \Ln \Rg f(x) } &\leq \seminorm{\Rg \Ln f (x) - \Rg \laplacian f(x)} + \seminorm{\Rg \laplacian f (x) - \Ln \Rg f(x)} =\\
			& =\seminorm{\Rg (\Ln f - \laplacian f ) (x)} + \seminorm{ \laplacian f' (x) - \Ln f'(x)} \leq \\
			& \leq \seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} + \seminorm{ \laplacian f' (x) - \Ln f'(x)}
	\end{align*}

Since $g^{-1}(x)\in\mathbb{S}^2$ and $f'$ still satisfies hypothesis, we can apply theorem \ref{theo:pointwise convergence for a regular sampling} to conclude that
\begin{align*}
 &\seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} \xrightarrow{n\to\infty}0\\
  &\seminorm{ \laplacian f' (x) - \Ln f'(x)}\xrightarrow{n\to\infty}0
\end{align*}
to conclude that $$\forall x\in\mathbb S^2 \quad\seminorm{\Rg \Ln f (x) - \Ln \Rg f(x) } \xrightarrow{n\to\infty}0$$

>>>>

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\renewcommand{\b}[1]{{\bm{#1}}}  % bold symbol
\newcommand{\bO}{\mathcal{O}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\S}{\mathbb{S}}
\newcommand{\G}{\mathcal{G}}  % graph
\newcommand{\V}{\mathcal{V}}  % vertex set
\newcommand{\E}{\mathcal{E}}  % edge set
\newcommand{\laplacian}{\Delta_{\mathbb S^2}}
\newcommand{\Rg}{\mathcal R_g}
\newcommand{\seminorm}[1]{\left|#1\right|}
\newcommand{\Ln}{\hat L_n^{t_n}}

@@

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. \mart{Here we insert the definition of the extended graph laplacian and of the rotation operator Rg} Following their setting, we define the extended graph Laplacian operator as a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$. Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere 
\begin{equation}\label{eq:rotation operator}
\mathcal R_g f(x) := f(g^{-1}(x)).
\end{equation}
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
	\end{equation*} 
% 	for $n\to\infty$.
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, the rescaled operator $\hat L_n^{t_n} := \frac{|\mathbb S^2|}{4\pi t^2}L_n^{t_n}$ (and its discrete counterpart $ \mathbf{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2} \mathbf L$) converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}. This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{prop}\label{prop:equivariance}
Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence for the rescaled graph Laplacian 
\begin{equation*}
\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{prop}
%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Proof of proposition \ref{prop:equivariance}}
\begin{proof}
Fix $x\in \mathbb S^2$. Since any rotation $\mathcal R_g$ is an isometry, and the Laplacian $\Delta$ commutes with all isometries of a Riemanniann manifold, and defining $\mathcal R_g f =: f'$ for ease of notation, we can write that 
	\begin{align*}
			\seminorm{\Rg \Ln f (x) - \Ln \Rg f(x) } &\leq \seminorm{\Rg \Ln f (x) - \Rg \laplacian f(x)} + \seminorm{\Rg \laplacian f (x) - \Ln \Rg f(x)} =\\
			& =\seminorm{\Rg (\Ln f - \laplacian f ) (x)} + \seminorm{ \laplacian f' (x) - \Ln f'(x)} \leq \\
			& \leq \seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} + \seminorm{ \laplacian f' (x) - \Ln f'(x)}
	\end{align*}

Since $g^{-1}(x)\in\mathbb{S}^2$ and $f'$ still satisfies hypothesis, we can apply theorem \ref{theo:pointwise convergence for a regular sampling} to say that
\begin{align*}
 &\seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} \xrightarrow{n\to\infty}0\\
  &\seminorm{ \laplacian f' (x) - \Ln f'(x)}\xrightarrow{n\to\infty}0
\end{align*}
to conclude that $$\forall x\in\mathbb S^2 \quad\seminorm{\Rg \Ln f (x) - \Ln \Rg f(x) } \xrightarrow{n\to\infty}0$$
